---
title: "QSRS"
author: "Stephen Leo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
library(ggplot2); library(rmarkdown)
```

## Model Setup

```{r data, echo=F}
setup <- c(paste0('Soil attribute: ', attribute),
           paste0('Version: ', version),
           paste0('Last updated: ', Sys.Date()),
           paste0('Depths modelled: ', paste(depths, collapse=', ')),
           paste0('Model: ', method_dsm),
           paste0('% of data used for training: ', propn_training*100),
           paste0('% of data used for testing: ', (1-propn_training)*100),
           paste0('Number of k-folds used in the cross-validation: ', k_kfold))
cat(setup, sep='\n')
```

Covariates used in model building

Covariate details can be found at https://aussoilsdsm.esoil.io/dsm-covariates/covariate-data

```{r covariates, echo=F}
paged_table(data.frame('Covariate' = sort(unique(gsub("\\d+$", "", ovi$Covariate)))))
```

## Training Data

Distribution of soil attribute data within each depth

```{r, echo=F}
DSM_data_depth <- data
DSM_data_depth <- DSM_data_depth %>% 
  pivot_longer(-!c(all_of(depths)), names_to = 'Depth', values_to = 'VALUE') %>% as.data.frame
DSM_data_depth <- DSM_data_depth %>% drop_na
DSM_data_depth$Depth = factor(DSM_data_depth$Depth, levels=c(depths))
ggplot(DSM_data_depth, aes(x=VALUE))+
  geom_histogram(aes(y=..density..), binwidth=.5, colour="black", fill="white")+
  facet_wrap(~ Depth, scales='free')+
  geom_vline(data=DSM_data_depth, aes(xintercept=mean(VALUE)),
               linetype="dashed", size=1, colour="red")+
  geom_density(alpha=.2, fill="red")+
  theme_bw()+labs(y='Density', x='Value')
```

Summary statistics of soil attribute data

```{r, echo=F}
sum_data <- data.frame(unclass(summary(na.omit(data))), check.names=F, stringsAsFactors=F, row.names=NULL)
paged_table(sum_data[c(1:2,4:ncol(sum_data))])
```

## Model Fitting Results - Each Depth Separately

The following results are from the generation of models for each depth separately.

Calibration dataset

List of metrics used:
- RMSE    =   root mean squared error
- R2      =   coefficient of determination
- MAE     =   mean absolute error
- MSE     =   mean squared error
- CC      =   Lin's concordance correlation coefficient
- Bias    =   mean bias
- RMedSE  =   root median squared error
- MedAE   =   median absolute error
- MedBias =   median bias

```{r cDat table, echo=F}
cDat <- read.csv(paste0(save_dir, '/GOOFData.csv'))
paged_table(cDat[1:length(depths),1:10])
```

```{r cDat, echo=F}
plot_data <- do.call(rbind, lapply(1:length(depths), function(i){
  read.csv(paste0(save_dir, '/', depths[i], '/cDat_GOOF.csv'))
}))
plot_data$Depth = factor(plot_data$Depth, levels=c(depths))
ggplot(plot_data, aes(Obs, Pred))+
  geom_point(size=0.5)+geom_abline(col='red', size=0.75)+geom_smooth(method='lm',formula='y ~ x', col='blue', size=0.75)+
  facet_wrap(~ Depth, scales='free')+
  theme_bw()
```

Validation dataset (i.e. unseen data)

```{r vDat table, echo=F}
vDat <- read.csv(paste0(save_dir, '/GOOFData.csv'))
paged_table(vDat[1:length(depths), c(1,11:19)])
```

```{r vDat, echo=F}
plot_data <- do.call(rbind, lapply(1:length(depths), function(i){
  read.csv(paste0(save_dir, '/', depths[i], '/vDat_GOOF.csv'))
}))
plot_data$Depth = factor(plot_data$Depth, levels=c(depths))
ggplot(plot_data, aes(Obs, Pred))+
  geom_point(size=0.5)+geom_abline(col='red', size=0.75)+geom_smooth(method='lm',formula='y ~ x', col='blue', size=0.75)+
  facet_wrap(~ Depth, scales='free')+
  theme_bw()
```

Variable importance

```{r vDat varimp, echo=F}
if(names(ovi[1]) != 'Covariate'){ovi <- dplyr::rename(ovi, Covariate = Row.names)}
ovi$Covariate <- gsub('_qld', '', ovi$Covariate)
paged_table(ovi)
```

## Example prediction map - Bundaberg region

```{r bundy, echo=F}
paste0(depths[1])
plot(prediction)
```

Bundaberg agricultural land

```{r bundy2, echo=F}
plot(prediction2)
```

Bundaberg city

```{r bundy3, echo=F}
plot(prediction3)
```
